---
title: "sf-fires-fire-dataset"
output: html_document
---

```{r}
library(data.table)
library(dplyr)
library(ggplot2)
library(ggmap)
library(reshape2)
library(broom)
library(maptools)
library(rgeos)
library(sp)
library(plm)
library(pglm)
```

##Reading in Data
```{r read data}
fires <- fread("data/Fire_Incidents.csv")
fires <- as.data.frame(fires)
zhvi <- read.csv("data/Neighborhood_Zhvi_AllHomes.csv")
```

##Paring down variables and observations in Fire Dataset
```{r cutting down fire dataset}
fires <- select(fires,c(Address, `Incident Date`, `Primary Situation`, Zipcode, `Estimated Property Loss`, `Property Use`, `Ignition Cause`, `Heat Source`, `Human Factors Associated with Ignition`, `Structure Type`, `Structure Status`, `Detectors Present`:`Location`)) %>%
# Singling out codes from data (incident codes and then property use)
  dplyr::mutate(situationcode = as.numeric(stringr::str_sub(`Primary Situation`, start = 1, end = 3))) %>%
  dplyr::mutate(propertycode = as.numeric(stringr::str_sub(`Property Use`, start = 1, end = 3))) %>%
#filtering by codes to use
dplyr::filter(situationcode %in% 100:118, situationcode != 112, propertycode %in% 400:429)
```
## Codes to Keep
Primary Situation: 100-118, excluding 112
Property Use: 400-429, 439- boarding/room house res.hotels?

```{r Recoding lat/long data}
fires <- reshape2::colsplit(fires$Location, ",", names = c("lat", "long"))%>%
  cbind(fires, .) %>%
  dplyr::mutate(lat = as.numeric(gsub("[(]", "", lat)), long = as.numeric(gsub("[)]", "", long)))

```


```{r geocode}
fires <- fires %>% dplyr::mutate(Address = tolower(paste(Address,"san francisco", sep = ", ")))

fires$index <- NA
fires[is.na(fires$lat),]$index <- seq(sum(is.na(fires$lat)))

taylor <- subset(fires,fires$index <= 1669)
kai <- subset(fires,fires$index > 1669)
```

```{r taylor geocode, include=FALSE}
#taylor will geocode this stuff
coord.taylor <- ggmap::mutate_geocode(taylor, Address)
saveRDS(coord.taylor,file = "coord-taylor.RDS")
```

```{r kai geocode, include=FALSE}
#
#
#kai will geocode this stuff
coord.kai <- ggmap::mutate_geocode(kai, Address)
saveRDS(coord.kai,file = "coord-kai.RDS")
#
#b4 running the rest, push RDS files to git
#
```

```{r geocode merge}
coord.kai <- readRDS("coord-kai.RDS")
coord.taylor <- readRDS("coord-taylor.RDS")

#fix lat and long vars
coord <- rbind(coord.kai,coord.taylor) %>%
  dplyr::mutate(lat = lat.1, long = lon, lat.1 = NULL, lon = NULL)
names(coord) <- names(fires)

#stick together with fires, sans the just coded data
fires <- fires[is.na(fires$index),]
fires <- fires %>% rbind(coord) 
```


```{r saving file }
saveRDS(fires, file = "Geocoded_fires.rds")
```

##Next Steps:
Exclude intentional fires, think about human factors in fire setting
How to plot count of fires by neighborhood--teach kai
Verify neighborhoods in both datasets-- do these match zillow nbhds?

##Done
Get Location data that is missing
Need to recode lat and long into useable format-- probs use str_split_fixed and sub or gsub hint: Location = (lat, long) 