---
title: "SF Fires"
author: "Kai Addae and Taylor Holdaway"
date: "May 21, 2016"
output: html_document
---

```{r bibliotheques}
library(data.table)
library(xlsx)
library(dplyr)
library(ggplot2)
library(ggmap)
library(reshape2)
library(broom)
library(maptools)
library(rgeos)
library(sp)
library(plm)
library(pglm)
```

```{r read data}
gfires <- readRDS("Geocoded_fires.rds")
nbhd.shape <- readRDS("nbhd_shape.rds")
zhvi.nbhd.df <- readRDS("zhvi_nbhd_df.rds")
```

```{r overlay fires to nbhds (aggregating)}
sp::coordinates(gfires) <- ~long + lat
t <- over(gfires, nbhd.shape)


```



Number of fires according to share of rent controlled living spaces in an area.

Number of fires according to property values (home values, rental prices, etc.)


##To Do:
1. Make list of "Primary Situation" codes that we intend to keep 
2. Make list of "Property Use" codes we intend to keep
3. Code location data for properties where it's missing
4. Clean Zillow data
5. Merge Zillow & Fires Data 
6. Come up with a model/hypothesis
7. REGRESS


##Data:
Zillow:
http://www.zillow.com/research/data/#rental-data
ZRI Time Series: Multifamily, SFR, Condo/Co-op ($)

SF Open City:
https://data.sfgov.org/Public-Safety/Fire-Incidents/wr8u-xric


