---
title: "SF Fires"
author: "Kai Addae and Taylor Holdaway"
date: "May 21, 2016"
output: html_document
---

```{r}
library(data.table)
library(dplyr)
library(ggplot2)
library(ggmap)

```

```{r}
fires <- fread("data/Fire_Incidents.csv",nrows = 10000)
fires <-  as.data.frame(fires)
zhvi <- read.csv("data/Neighborhood_Zhvi_AllHomes.csv")
```

```{r Cleaning Fires}
f <- select(fires,c(Address, `Incident Date`, `Primary Situation`, Zipcode, `Estimated Property Loss`, `Property Use`, `Ignition Cause`, `Heat Source`, `Human Factors Associated with Ignition`, `Structure Type`, `Structure Status`, `Detectors Present`:`Location`))
```
To Do:
1. Make list of "Primary Situation" codes that we intend to keep
2. Make list of "Property Use" codes we intend to keep
3. Code location data for properties where it's missing
4. Clean Zillow data
5. Merge Zillow & Fires Data
6. Come up with a model/hypothesis  
7. REGRESS



Number of fires according to share of rent controlled living spaces in an area.

Number of fires according to property values (home values, rental prices, etc.)


##Data:
Zillow:
http://www.zillow.com/research/data/#rental-data
ZRI Time Series: Multifamily, SFR, Condo/Co-op ($)

SF Open City:
https://data.sfgov.org/Public-Safety/Fire-Incidents/wr8u-xric
