---
title: "SF Fires"
author: "Kai Addae and Taylor Holdaway"
date: "May 21, 2016"
output: html_document
---

```{r bibliotheques}
library(dplyr)
library(ggplot2)
library(ggmap)
library(reshape2)
library(broom)
library(maptools)
library(rgeos)
library(sp)
```

```{r read data}
gfires <- readRDS("rdata/Geocoded_fires.rds")
nbhd.shape <- readRDS("rdata/nbhd_shape.rds")
zhvi.nbhd.df <- readRDS("rdata/zhvi_nbhd_df.rds")
```

```{r overlay fires to nbhds (aggregating)}
sp::coordinates(gfires) <- ~long + lat
t <- over(gfires, nbhd.shape)
#note rownames of df from sp::over match rownames from spdf (gfires spdf). see this by:
#sum(rownames(gfires@data) != rownames(t))
#so just use cbind to bind cols of the two dataframes:
gfires@data <- cbind(gfires@data,t)
#note that the neighborhood variable from the original fire data and the neighborhood variable from the overlay sometimes do not agree. chock this up to differently defined neighborhoods between zillow and the inputter of the sf fire data
gfires <- gfires[nbhd.shape,]
#AGGREGATION
gfires2 <- gfires@data %>% dplyr::group_by( ., year, month, NAME, REGIONID) %>%
  summarize(countoffires = n())
```

```{r merge zillow & fires data}

```


Number of fires according to share of rent controlled living spaces in an area.

Number of fires according to property values (home values, rental prices, etc.)


##To Do:
Clean Zillow data
Merge Zillow & Fires Data 
* Exclude Fires in single family units
* get ACS data
* clean ACS data, combine tracts to form nbhds
* merge ACS data with zillow/fires data
*Come up with a model/hypothesis
*REGRESS


##Data:
Zillow:
http://www.zillow.com/research/data/#rental-data
ZRI Time Series: Multifamily, SFR, Condo/Co-op ($)

SF Open City:
https://data.sfgov.org/Public-Safety/Fire-Incidents/wr8u-xric


